\documentclass[letterpaper,12pt]{article}
\usepackage{tabularx} % extra features for tabular environment
\usepackage{amsmath}  % improve math presentation
\usepackage{graphicx} % takes care of graphic including machinery
\usepackage[margin=1in,letterpaper]{geometry} % decreases margins
\usepackage{cite} % takes care of citations
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{fixmath}
\usepackage{amsmath}
\usepackage{amssymb}
\newcommand{\R}{\mathbb{R}}
\usepackage[final]{hyperref} % adds hyper links inside the generated pdf file
\hypersetup{
	colorlinks=true,       % false: boxed links; true: colored links
	linkcolor=blue,        % color of internal links
	citecolor=blue,        % color of links to bibliography
	filecolor=magenta,     % color of file links
	urlcolor=blue         
}
\usepackage{gensymb}
\usepackage{blindtext}
%++++++++++++++++++++++++++++++++++++++++


\begin{document}

\title{Robotics and Deep Learning}
\author{Michele Antonazzi}
\date{\today}
\maketitle

\begin{abstract}
This work is an overview concerning robotics and the machine learning applications can have on it, with a particular focus on deep learning.  
\end{abstract}

\input{introduction.tex}
\newpage

\input{article_1.tex}
\newpage

\input{article_2.tex}
\newpage

\input{article_3.tex}
\newpage

\input{article_4.tex}
\newpage

\input{article_5.tex}
\newpage

\input{article_6.tex}
\newpage

\input{article_7.tex}
\newpage

\input{article_8.tex}
\newpage

\input{article_9.tex}
\newpage

\input{article_10.tex}
\newpage


\begin{thebibliography}{99}
\bibitem{} Niko Sünderhauf, Oliver Brock, Walter Scheirer, Raia Hadsell,
Dieter Fox, Jürgen Leitner, Ben Upcroft, Pieter Abbeel, Wolfram Burgard,
Michael Milford, Peter Corke, ``The Limits and Potentials of Deep
Learning for Robotics", eprint arXiv:1804.06557, April 2018

\bibitem{} A. Giusti \emph{et al}., ``A Machine Learning Approach to Visual
Perception of Forest Trails for Mobile Robots," in \emph{IEEE Robotics
	and Automation Letters}, vol. 1, no. 2, pp. 661-667, July 2016, doi:
10.1109/LRA.2015.2509024.

\bibitem{} P. Santana, L. Correia, R. Mendonça, N. Alves, and J. Barata,
``Tracking natural trails with swarm-based visual saliency," J. Field
Rob., vol. 30, no. 1, pp. 64--86, 2013.

\bibitem{} M. Chancán, L. Hernandez-Nunez, A. Narendra, A. B. Barron and M.
Milford, ``A Hybrid Compact Neural Architecture for Visual Place
Recognition," in \emph{IEEE Robotics and Automation Letters}, vol. 5,
no. 2, pp. 993-1000, April 2020, doi: 10.1109/LRA.2020.2967324.

\bibitem{} A. Magassouba, K. Sugiura, A. Trinh Quoc, and H. Kawai,
``Understanding natural language instructions for fetching daily objects
using GAN-based multimodal target-source classification," IEEE Robot.
Autom. Lett., vol. 4, no. 4, pp. 3884--3891, Oct. 2019.

\bibitem{} H. Fukui, T. Hirakawa, T. Yamashita, and H. Fujiyoshi,
``Attention branch network: Learning of attention mechanism for visual
explanation," in Proc. CVPR, 2019, pp. 10 705--10 714.

\bibitem{} J. Hatori et al., ``Interactively picking real-world objects with
unconstrained spoken language instructions," in Proc. IEEE ICRA, 2018,
pp. 3774--3781.

\bibitem{} A. Palffy, J. Dong, J. F. P. Kooij and D. M. Gavrila, ``CNN Based
Road User Detection Using the 3D Radar Cube," in \emph{IEEE Robotics and
	Automation Letters}, vol. 5, no. 2, pp. 1263-1270, April 2020, doi:
10.1109/LRA.2020.2967272.

\bibitem{} W. Liu et al., ``SSD: Single shot multibox detector," Lecture
Notes in Computer Science (including subseries Lecture Notes in
Artificial Intelligence and Lecture Notes in Bioinformatics), vol. 9905
LNCS, pp. 21--37, 2016.

\bibitem{} R. Prophet et al., ``Pedestrian classification with a 79 GHz
automotive radar sensor,'' in Proc. 19th Int. Radar Symp., 2018, pp.
1--6.

\bibitem{} O. Schumann, M. Hahn, J. Dickmann, and C. Wöhler, ``Comparison
of random forest and long short-term memory network performances in
classification tasks using radar," in Proc. Sensor Data Fusion: Trends,
Solutions, Appl., 2017, pp. 1--6.

\bibitem{} A. Kurobe, Y. Sekikawa, K. Ishikawa and H. Saito, ``CorsNet: 3D
Point Cloud Registration by Deep Neural Network," in \emph{IEEE Robotics
	and Automation Letters}, vol. 5, no. 3, pp. 3960-3966, July 2020, doi:
10.1109/LRA.2020.2970946.

\bibitem{} P. J. Besl and N. D. McKay, ``Method for registration of 3-d
shapes," in Proc. Sensor Fusion IV: Control Paradigms Data Struct.,
1992, vol. 1611, 1992, pp. 586--607.

\bibitem{} C. R. Qi, H. Su, K. Mo, and L. J. Guibas, ``Pointnet: Deep
learning on point sets for 3d classification and segmentation," in Proc.
IEEE Conf. Comput. Vis. Pattern Recognit., 2017, pp. 652--660.

\bibitem{} Y. Aoki, H. Goforth, R. A. Srivatsan, and S. Lucey,
``Pointnetlk: Robust \& efficient point cloud registration using
pointnet," IEEE Conf. Comput. Vis. Pattern Recog. (CVPR), Jun. 2019.

\bibitem{} Z. Wu et al., ``3D shapenets: A deep representation for
volumetric shapes," in Proc. IEEE Conf. Comput. Vis. Pattern Recognit.,
2015, pp. 1912--1920.

\bibitem{} M. Mancini, S. R. Bulò, E. Ricci and B. Caputo, ``Learning Deep
NBNN Representations for Robust Place Categorization," in \emph{IEEE
	Robotics and Automation Letters}, vol. 2, no. 3, pp. 1794-1801, July
2017, doi: 10.1109/LRA.2017.2705282.

\bibitem{} I. Kuzborskij, F. Maria Carlucci, and B. Caputo, ``When naive
bayes nearest neighbors meet convolutional neural networks," in Proc.
IEEE Conf. Comput. Vis. Pattern Recognit., 2016, pp. 2100--2109.

\bibitem{} A. Krizhevsky, I. Sutskever, and G. E. Hinton, ``Imagenet
classification with deep convolutional neural networks," in Proc. 25th
Int. Conf. Neural Inf. Process. Syst., 2012, pp. 1097--1105.

\bibitem{} Y. Jia et al., ``Caffe: Convolutional architecture for fast
feature embedding," in Proc. 22nd ACM Int. Conf. Multimedia, 2014, pp.
675--678.

\bibitem{} K. Simonyan and A. Zisserman, ``Very deep convolutional networks
for large-scale image recognition," 2014, arXiv preprint arXiv:
1409.1556.

\bibitem{} C. Szegedy et al., ``Going deeper with convolutions," in Proc.
IEEE Conf. Comput. Vis. Pattern Recognit., 2015, pp. 1--9.

\bibitem{} B. Zhou, A. Lapedriza, J. Xiao, A. Torralba, and A. Oliva,
``Learning deep features for scene recognition using places database," in
Proc. 27th Int. Conf. Neural Inf. Process. Syst., 2014, pp. 487--495.

\bibitem{} B. Zhou, A. Khosla, A. Lapedriza, A. Torralba, and A. Oliva,
``Places: An image database for deep scene understanding," 2016, arXiv
preprint arXiv: 1610.02055.

\bibitem{}A. Pronobis, B. Caputo, P. Jensfelt, and H. I. Christensen, ``A
discriminative approach to robust visual place recognition," in Proc.
IEEE/RSJ Int. Conf. Intell. Robots Syst., 2006, pp. 3829--3836.

\bibitem{} J. Wu and J. M. Rehg, ``Centrist: A visual descriptor for scene
categorization," IEEE Trans. Pattern Anal. Mach. Intell., vol. 33, no.
8, pp. 1489--1501, Aug. 2011.

\bibitem{} E. Fazl-Ersi and J. K. Tsotsos, ``Histogram of oriented uniform
patterns for robust place recognition and categorization," Int. J.
Robot. Res., vol. 31, no. 4, pp. 468--483, 2012.

\bibitem{} P. Hu, D. Held and D. Ramanan, ``Learning to Optimally Segment
Point Clouds," in \emph{IEEE Robotics and Automation Letters}, vol. 5,
no. 2, pp. 875-882, April 2020, doi: 10.1109/LRA.2020.2965389.

\bibitem{} A. Magassouba, K. Sugiura and H. Kawai, ``A Multimodal
Target-Source Classifier With Attention Branches to Understand Ambiguous
Instructions for Fetching Daily Objects," in IEEE Robotics and
Automation Letters, vol. 5, no. 2, pp. 532-539, April 2020, doi:
10.1109/LRA.2019.2963649.

\bibitem{} D. Held, D. Guillory, B. Rebsamen, S. Thrun, and S. Savarese,
``A probabilistic framework for real-time 3D segmentation using spatial,
temporal, and semantic cues," Robotics: Science and Systems, 2016.

\bibitem{} J. Chen, Y. K. Cho and Z. Kira, ``Multi-View Incremental
Segmentation of 3-D Point Clouds for Mobile Robots," in \emph{IEEE
	Robotics and Automation Letters}, vol. 4, no. 2, pp. 1240-1246, April
2019, doi: 10.1109/LRA.2019.2894915.

\bibitem{} C. R. Qi, L. Yi, H. Su, and L. J. Guibas, ``Pointnet++: Deep
hierarchical feature learning on point sets in a metric space,"
arXiv:1706.02413, 2017.

\bibitem{} D. Maturana and S. Scherer, ``VoxNet: A 3D convolutional neural
network for real-time object recognition," in Proc. IEEE/RSJ Int. Conf.
Intell. Robot Syst., 2015, pp. 922--928.

\bibitem{} W. Wang, R. Yu, Q. Huang, and U. Neumann, ``SGPN: Similarity
group proposal network for 3D point cloud instance segmentation," in
Proc. IEEE Conf. Comput. Vis. Pattern Recognit., Jun. 2018, pp.
2569--2578.

\bibitem{} N. X. Vinh, J. Epps, and J. Bailey, ``Information theoretic
measures for clusterings comparison: Variants, properties, normalization
and correction for chance,'' J. Mach. Learn. Res., vol. 11, pp.
2837--2854, Dec. 2010. {[}Online{]}. Available:
http://dl.acm.org/citation.cfm?id=1756006.1953024.

\bibitem{} S. Gomez-Gonzalez, S. Prokudin, B. Schölkopf and J. Peters,
``Real Time Trajectory Prediction Using Deep Conditional Generative
Models," in \emph{IEEE Robotics and Automation Letters}, vol. 5, no. 2,
pp. 970-976, April 2020, doi: 10.1109/LRA.2020.2966390.

\bibitem{} K. Mülling, J. Kober, and J. Peters, ``A biomimetic approach to
robot table tennis," Adaptive Behav., vol. 19, no. 5, pp. 359--376,
2011.

\bibitem{} X. Chen et al., ``A robust vision module for humanoid robotic
ping-pong game," Int. J. Adv. Robot. Syst., vol. 12, no. 4, 2015, Art.
no. 35.

\bibitem{} S. Gomez-Gonzalez, G. Neumann, B. Schölkopf, and J. Peters,
``Adaptation and robust learning of probabilistic movement primitives,"
Aug. 2018, arXiv:1808.10648.

\end{thebibliography}


\end{document}